---
title: "Lab05Solution"
author: "Frank Guo"
date: "2024-04-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1: Generate simulated data sets.   

## Step 1.1: Generate the data sets.   

```{r echo=TRUE,include=FALSE}

# load libraries
library(glmnet)
library(MASS)
library(tidyverse)
# set up parameters
set.seed(230) 
n <- 80  
p <- 80  
lambdas <- 2^ seq(6, -4, length = 100)  # lambda values.
# set up correlation matrix between Xs.?
cor.mat <- matrix(0.7, nrow = p, ncol = p)
diag(cor.mat) <- 1
cor.mat[lower.tri(cor.mat)] <- t(cor.mat)[lower.tri(cor.mat)]
# dat_A
X1 <- mvrnorm(n, mu=rep(1, p), Sigma = cor.mat)
colnames(X1) <- paste0('X', str_pad(1:p, nchar(p), 'left', '0'))
n_betas <- 5
betas <- as.vector(scale(sample(1:n_betas))) * 10
related.ind <- sample(1:p, n_betas)
y1 <- as.numeric(betas %*% t(X1[,related.ind]) + rnorm(n))
dat_A <- cbind(data.frame(Y = y1), X1)
# dat_B 
X2 <- mvrnorm(n, mu=rep(1, p), Sigma = cor.mat)
colnames(X2) <- paste0('X', str_pad(1:p, nchar(p), 'left', '0'))
all_betas <- sample(as.vector(scale(1:p))) * 0.1
y2 <- as.numeric(all_betas %*% t(X2) + rnorm(n))
dat_B <- cbind(data.frame(Y = y2), X2)
  
```

## Step 1.2: Understand the code
what is the similarity and difference between the two data sets, dat_A and dat_B?     


### Answer:    

dat_A and dat_B has the same predictors generated by mvrnorm with the mean=1 and
highly correlated to each other.    

But the dependent variable of dat_A heavy related to five of predictors. and dat_A 
equally related to all the predictors.    


## Step 1.3: Split into train and test.   

```{r echo=TRUE}

train_ind <- sample(1:n, ceiling(0.8*n))
test_ind <- (1:n)[-train_ind]

train_data_A <- dat_A[train_ind,]
test_data_A <- dat_A[test_ind,]

train_data_B <- dat_B[train_ind,]
test_data_B <- dat_B[test_ind,]


```



```{r}
# 创建一个包含身高和体重的数据框
data <- data.frame(
  height = c(160, 170, 165, 180, 175), # 身高（单位：厘米）
  weight = c(60, 70, 65, 80, 75)        # 体重（单位：千克）
)

# 打印原始数据
print("原始数据：")
print(data)

# 使用scale函数对数据进行标准化处理
scaled_data <- scale(data)

# 打印标准化后的数据
print("标准化后的数据：")
print(scaled_data)

```

